Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-16 paper.tex
add dacapo and start bench

\paragraph{ExpandPropertiesWithCache.} The ExpandPropertiesWithCache benchmark does not increase the overall memory size. Since the compacting GC has compacted the heap before starting the benchmark, there is enough room to allocate the large objects (large objects are allocated directly in old space) required by the benchmark and there is no need for a full GC during the benchmark. However, with the sweep algorithm, there are multiple small available memory chunks which are not big enough to hold all the requested large objects, so a full GC is required. In addition, execution time is worse, as for the previous benchmark.

@@

\paragraph{FragmentedHeap.}
\paragraph{LargeObjects.}
\paragraph{Data0bjects.}

@@

\paragraph{GC benchmark suite.}
Dacapo + see ref in Dacapo. \cite{DacapoBench}
\todo{Sophie}

\paragraph{ACDC-JS.}
ACDC-JS \cite{ACDCJS} is a configurable benchmarking tool designed to specifically measure and stress allocation and deallocation time in the JavaScript memory management model. 
It builds a heap model based on the behavior of real-time applications and aims at providing significant insights on the JavaScript memory management that cannnot be obtained from standard benchmarking suites. The value of specific heap options can be set by the user. 
Their study shows the negative impact of object liveness (time between allocation and last access, leading to the objects to be in different spaces in the heap) and deallocation delay on allocation time. It also stresses the trade-offs between memory consumption and allocation latency.

>>>>

\paragraph{ExpandPropertiesWithCache.} The ExpandProperties WithCache benchmark does not increase the overall memory size. Since the compacting GC has compacted the heap before starting the benchmark, there is enough room to allocate the large objects (large objects are allocated directly in old space) required by the benchmark and there is no need for a full GC during the benchmark. However, with the sweep algorithm, there are multiple small available memory chunks which are not big enough to hold all the requested large objects, so a full GC is required. In addition, execution time is worse, as for the previous benchmark.

@@

\paragraph{FragmentedHeap.} 
\begin{itemize}
\item impact on memory size and numbers of segments
\item impact on execution time 
\end{itemize}
\paragraph{LargeObjects.}
\begin{itemize}
\item impact on memory size 
\item impact on number of scavenges and number of full GC's
\end{itemize}
\paragraph{Data0bjects.}
\begin{itemize}
\item impact on memory size
\item impact on overall time (full gc, compaction time)
\end{itemize}

@@

\paragraph{GC benchmark suite.} The DaCapo benchmarks \cite{DacapoBench} is a standard benchmarking suite designed for Java applications. It gathers several open-source benchmarks and run them against specific metrics to assess their potential performance \sk{significance towards} on different aspects of the Java language, typically its memory management and virtual machines.
With regard to memory management, the eleven benchmarks selected in 2006 (and updated later in 2009, to add three more benchmarks \ref{dacapowebsite} \sk{add ref in bib}) are assessed according to their number of allocated objects and their average size and their maximum number of live objects. The nursery (young space) survival rate is also taken into account, as well as the heap structure through object lifetime behavior.
These criteria were chosen \sk{rephrase} as significant to asses the performance of memory management.

%The part dedicated to memory management focuses on three metrics: allocation demographics, lifetime and live objects. The benchmarks used shows a rich and diverse object lifetime behaviors. --> dacapo allocates more objets, 3 time the live size of SPEC.
%Heap volume, Heap objects, Mean object size, nursery survival rate.
%
%measure object size demographics (size demographics for each benchmark)
%--> live and allocation time serie analysis
%plot heap composition (allocations and pointer mutations)
%--> richer lifetime behavior

\paragraph{ACDC-JS.}
ACDC-JS \cite{ACDCJS} is a configurable \\benchmarking tool designed to specifically measure and stress allocation and deallocation time in the JavaScript memory management model. 
It builds a heap model based on the behavior of real-time applications and aims at providing significant insights on the JavaScript memory management that cannnot be obtained from standard benchmarking suites. The value of specific heap options can be set by the user. 
Their study shows the negative impact of object liveness (time between allocation and last access, leading to the objects to be in different spaces in the heap) and deallocation delay on allocation time. It also stresses the trade-offs between memory consumption and allocation latency.
